---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pligFx

<!-- badges: start -->
<!-- badges: end -->

The goal of pligFx is to ...

## Installation

You can install the development version of pligFx from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kennedynyavor/PligFx",force = TRUE)
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(pligFx)
library(tidyverse)
## basic example code
```

The `read_pmt` function imports the all payment data seemlessly and performs all neccesary joins internally. It takes the production month and a `data_after` parameter. Data_after is used to filter the all payment data (payment_date >= data_after).

```{r cars}
setwd("~/z_data/data_prep/")
df <- read_pmt(as.Date("2024-11-01"))
```

Check the import

```{r pressure, echo = FALSE}
df %>% 
  group_by(allocation_month,product_type) %>% 
  summarise(GwP = sum(amount)) %>% 
  filter(year(allocation_month)==2016)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
